---
title: "analyses policy new"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: lumen
    toc: yes
    toc_depth: 4
    number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(class.source = "CSSoutput",
                      eval = TRUE, echo = FALSE, include = TRUE,warning=FALSE,
                      fig.align='center', fig.show='asis',  fig.width = 16, fig.height = 10,
                      size='footnotesize')

```


```{r packages, include=FALSE}
setwd("/Users/nfrings/Library/Mobile Documents/com~apple~CloudDocs/Documents/PhD/Studies/Winter studie/results")
#setwd("/Users/ninafrings/Documents/PhD/Studies/Winter studie/results")

library(tidyverse)
library(sjPlot)
library(rcompanion)
library(rstatix)
library(lmerTest); library(lme4)
library(sjlabelled)
library(sjmisc)
library(emmeans)
library("rmcorr")
library(psych)
library(patchwork)
library(afex)
library(ggeffects)

# so plot_model plots look nice
set_theme(base=theme_classic())
```


```{r data, include=FALSE}
#### wave 1 ###

data.decision.waves.long <- read_csv("wave 2 and both waves/data/data.decision.waves.long.csv")
data.decision.waves.long <- data.decision.waves.long[,-c(1)]

data.decision.waves.long$gender <- factor(data.decision.waves.long$gender)
data.decision.waves.long$country <- factor(data.decision.waves.long$country)
data.decision.waves.long <- data.decision.waves.long %>% filter(!gender=="non-binary")
data.decision.waves.long$income <- factor(data.decision.waves.long$income,
                                          levels=c( "<1'500€\n<3'100CHF","<1'500- 2'499€\n3'100-4'299CHF", "2'500- 4'000€\n<4'300- 5'899CHF", "> 4'000€\n>5'900 CHF") )

data.decision.waves.long$education <- factor(data.decision.waves.long$education,
                                             levels=c("no formal education", "obligatory school", "middle school" , "degree"))
data.decision.waves.long$decision <- factor(data.decision.waves.long$decision)

data.decision.waves.long$wave <- factor(data.decision.waves.long$wave, levels=c("wave1", "wave2"), labels=c("Wave 1", "Wave 2"))
data.decision.waves.long$co2 <- factor(data.decision.waves.long$co2)
data.decision.waves.long$tax <- factor(data.decision.waves.long$tax)
data.decision.waves.long$energieabhaengigkeit <- factor(data.decision.waves.long$energieabhaengigkeit)
data.decision.waves.long$zeitpunkt <- factor(data.decision.waves.long$zeitpunkt, 
                                             labels=c("in 1 year", "in 7 years"))

```


```{r wave1}
### wave 1 ####
data.decision <- data.decision.waves.long %>% filter (wave=="Wave 1")

#### H1 ####
## All policy attributes significantly predict policy decisions
## H1: run a logistic model with random intercept for id.controlled for age, gender, country of origin and income.
# for plotting later set labels now
set_label(data.decision$tax) <- "tax (1% vs 6%)"
set_label(data.decision$energieabhaengigkeit) <- "energyindependence (10% vs 20%)"
set_label(data.decision$co2) <- "CO2 reduction (15% vs 30%)"
set_label(data.decision$zeitpunkt) <- "implementation (in 1 vs 7 years)"


model.H1.pre_reg <- glmer(decision~ co2 + tax + energieabhaengigkeit + zeitpunkt  +
                            age + gender + income.wave1 + country + education +
                            (1 | m),
                          data=data.decision, family="binomial")

## random slope for attributes
model.H1.random_s.d <- glmer(decision~ co2 + tax + energieabhaengigkeit + zeitpunkt  +
                               age + gender + income.wave1 + country + education + 
                               (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                             data=data.decision, family="binomial")

# without demographics for better overview 
model.H1.random_s <- glmer(decision~ co2 + tax + energieabhaengigkeit + zeitpunkt  +
                             (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                           data=data.decision, family="binomial")
```
## wave 1 
### H1 {.tabset}
#### H1 pre-registered
Model with random intercept and demographics
```{r}
tab_model(model.H1.pre_reg)
```
#### H1 random slopes
Model with random slope and demographics
```{r}
tab_model(model.H1.random_s.d)
```
#### H1 random slopes no demographics

```{r}
tab_model(model.H1.random_s)

```

### H1b {.tabset}
```{r}
### H1b ####
## adding climate change concern

## pre-reg model
model.H1b.pre_reg <- glmer(decision~ co2 + tax + energieabhaengigkeit +
                             (zeitpunkt * concern.scaled) +
                             age + gender + income.wave1 + country + education +
                             (1  | m),
                           data = data.decision,family = binomial(link = "logit"))

model.H1b.sd<- glmer(decision~ co2 + tax + energieabhaengigkeit +
                       (zeitpunkt * concern.scaled) +
                       age + gender + income.wave1 + country + education +
                       (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                     data = data.decision,family = binomial(link = "logit"))


```

#### H1b pre-reg
```{r}
tab_model(model.H1b.pre_reg)

```

#### H1b random slopes
```{r}
tab_model(model.H1b.sd)

```

### H1 c {.tabset}
```{r}
#### H1c ####
data.H1c <- read.csv("wave1 results and R/data/data.model.co2.c.csv")
data.H1c <- data.H1c %>%
  rename( co2.beta= "co2.30..CO2",
          tax.beta= "tax.6.",
          energy.beta = "energieabhaengigkeit.20."  ,
          time.beta =  "zeitpunktin.7.Jahren"     )
data.H1c$co2.beta.n <- as.numeric(data.H1c$co2.beta)
data.H1c$education <- factor(data.H1c$education,
                             levels=c("no formal education", "obligatory school", "middle school",  "degree") )
data.H1c$income <- factor(data.H1c$income,
                          levels=c( "<1'500€\n<3'100CHF","<1'500- 2'499€\n3'100-4'299CHF", "2'500- 4'000€\n<4'300- 5'899CHF", "> 4'000€\n>5'900 CHF") )
data.H1c$gender <- factor(data.H1c$gender)
data.H1c <- data.H1c %>% filter(!gender=="non-binary")
describe(data.H1c$co2.beta.n) # range = -0.64 1.54
# this means in OR's from 0.52 to 4.66 OR

set_label(data.H1c$concern.scaled) <-  "climate change concern (scaled)"
set_label(data.H1c$co2.beta.n) <-  "CO2 attribute importance"

# model cc concern
model.cc.d <- lm(co2.beta.n ~  gender + age + income + country + education +
                   climate_concern , data=data.H1c )

# outliers?
# mean ± 3sd
mean(data.H1c$co2.beta.n) + 3 *sd(data.H1c$co2.beta.n)
data.H1c.excl <- data.H1c %>% filter(co2.beta.n > -0.5718221) %>% filter(co2.beta.n < 1.610175)


### rerun model with limit
model.cc.d.excl <- lm(co2.beta.n ~  gender + age + income + country +
                        concern.scaled, data=data.H1c.excl )


```
#### H1 c wave 1
```{r}
tab_model(model.cc.d, digits=3)
```

#### H1 c wave1 excluding extremes
```{r}
tab_model(model.cc.d.excl,digits=3)
```


```{r}
#H1c across both waves

data.H1c.waves <- read.csv("wave 2 and both waves/data/data.model.co2.waves.csv")
data.H1c.waves <- data.H1c.waves %>%
  rename( co2.beta= "co2.30..CO2",
          tax.beta= "tax.6.",
          energy.beta = "energieabhaengigkeit.20."  ,
          time.beta =  "zeitpunktin.7.years"     )
data.H1c.waves$co2.beta.n <- as.numeric(data.H1c.waves$co2.beta)
data.H1c.waves$education <- factor(data.H1c.waves$education,
                             levels=c("no formal education", "obligatory school", "middle school",  "degree") )
data.H1c.waves$income <- factor(data.H1c.waves$income,
                          levels=c( "<1'500€\n<3'100CHF","<1'500- 2'499€\n3'100-4'299CHF", "2'500- 4'000€\n<4'300- 5'899CHF", "> 4'000€\n>5'900 CHF") )
data.H1c.waves$gender <- factor(data.H1c.waves$gender)
data.H1c.waves <- data.H1c.waves %>% filter(!gender=="non-binary")
describe(data.H1c.waves$co2.beta.n) # range = -0.64 1.54
# this means in OR's from 0.52 to 4.66 OR

set_label(data.H1c.waves$concern.scaled) <-  "climate change concern (scaled)"
set_label(data.H1c.waves$co2.beta.n) <-  "CO2 attribute importance"

# model cc concern
model.cc.d.waves <- lm(co2.beta.n ~  wave +  gender + age + income + country + education +
                   concern.scaled , 
                   data=data.H1c.waves )

# outliers?
# mean ± 3sd
mean(data.H1c.waves$co2.beta.n) + 3 *sd(data.H1c$co2.beta.n)
data.H1c.waves.excl <- data.H1c.waves %>% filter(co2.beta.n > -0.5718221) %>% filter(co2.beta.n < 1.610175)


### rerun model with limit
model.cc.d.both.excl <- lm(co2.beta.n ~  gender + age + income + country +
                        concern.scaled, data=data.H1c.waves.excl )



```

#### H1c both waves
```{r}
tab_model(model.cc.d.waves, digits=3)

```

#### H1 c both waves excluding extremes
```{r}
tab_model(model.cc.d.both.excl)

```


## wave 2 
### H1  {.tabset}

```{r wave2}
### wave 2 ####
data.decision.wave2 <- data.decision.waves.long %>% filter (wave=="Wave 2")

# for plotting later set labels now
set_label(data.decision.wave2$tax) <- "tax (1% vs 6%)"
set_label(data.decision.wave2$energieabhaengigkeit) <- "energyindependence (10% vs 20%)"
set_label(data.decision.wave2$co2) <- "CO2 reduction (15% vs 30%)"
set_label(data.decision.wave2$zeitpunkt) <- "implementation (in 1 vs 7 years)"

## random slope no demographics
model.H1.random_s.wave2 <- glmer(decision~ co2 + tax + energieabhaengigkeit + zeitpunkt  +
                                   (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                                 data=data.decision.wave2, family="binomial")

model.H1.random_s.d.wave2 <- glmer(decision~ co2 + tax + energieabhaengigkeit + zeitpunkt  +
                                     age + gender + income.wave2  + country + education +
                                     (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                                   data=data.decision.wave2, family="binomial")

## random intercept and demographics
model.H1.wave2.d <- glmer(decision~ co2 + tax + energieabhaengigkeit + zeitpunkt  +
                            age + gender + income.wave2  + country + education +
                            (1 | m),
                          data=data.decision.wave2, family="binomial")

```

#### H1 prereg
```{r}
tab_model(model.H1.wave2.d)

```

#### H1 random slopes
```{r}
tab_model(model.H1.random_s.d.wave2)
```

#### H1 random slopes no demographics
```{r}
tab_model(model.H1.random_s.wave2)

```

### H1b {.tabset}

```{r}
### H1b ### (preregistered)
# adding climate change concern
model.H1b.wave2 <- glmer(decision~ co2 + tax + energieabhaengigkeit +
                           (zeitpunkt * concern.scaled) +
                           age + gender + income.wave2  + country + education +
                           (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                         data = data.decision.wave2,family = binomial(link = "logit"))

model.H1b.wave2.d <- glmer(decision~ co2 + tax + energieabhaengigkeit +
                             (zeitpunkt * concern.scaled) +
                             age + gender + income.wave2  + country + education +
                             (1 | m),
                           data = data.decision.wave2,family = binomial(link = "logit"))
```

#### H1b prereg
```{r}
tab_model(model.H1b.wave2.d)

```
#### H1b random slopes
```{r}
tab_model(model.H1b.wave2)

```

## Comparisons between waves

### H1 plot both waves
```{r fig1a}
### comparisons between waves ####

### plot all ORs in one plot for each wave

Figure1a <- plot_models(model.H1.random_s, model.H1.random_s.wave2,  m.labels =c("Wave 1", "Wave 2"), legend.title="assessment waves", colors=c("#15A000", "#0070C0"), axis.lim = c(0.01,2),
                        axis.labels = c(paste0("Implementation", "\n", "time"), paste0("Energy", "\n" ,"independence"),
                                        "Taxes", paste0("Co2 reduction", "\n", "potential") )) + labs(title="a", color="Assessment wave") +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19))
Figure1a
```


### H1 across waves {.tabset}
```{r bothwaves}
## H1 across waves with demographics , random slope and wave as predictor, main effect 
model.both.waves.2.c <- glmer(decision~ wave + co2 + tax + energieabhaengigkeit + zeitpunkt   +
                                country + age + gender + education + income +
                                (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                              data = data.decision.waves.long,family = binomial(link = "logit") )

## H1 across waves without demographics , random slope and wave as predictor, main effect (reported)
model.both.waves.2.rep <- glmer(decision~ wave + co2 + tax + energieabhaengigkeit + zeitpunkt   +
                                  (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                                data = data.decision.waves.long,family = binomial(link = "logit") )

## H1 across waves with demographics , random intercept 
model.both.waves.i.d <- glmer(decision~ wave + co2 + tax + energieabhaengigkeit + zeitpunkt   +
                                country + age + gender + education + income +
                                (1 | m),
                              data = data.decision.waves.long,family = binomial(link = "logit") )

```

#### H1 both waves prereg
```{r}
tab_model(model.both.waves.i.d)

```
#### H1 both waves random slopes
```{r}
tab_model(model.both.waves.2.c)

```
#### H1 both waves random slopes no demographics
```{r}
tab_model(model.both.waves.2.rep)

```


### H1b across waves {.tabset}

```{r}
#### H1b across both waves, only 1 plot ####
## random slope with demographics
model.H1b.both.waves2.d <- glmer(decision~  wave + energieabhaengigkeit + tax + co2 + zeitpunkt*concern.scaled  +
                                   country + age + gender + education + income + 
                                   (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                                 data = data.decision.waves.long, family = binomial(link = "logit"))

# with random intercept instead and demographics
model.H1b.both.waves2.i.d <- glmer(decision~  wave + energieabhaengigkeit + tax + co2 + zeitpunkt*concern.scaled  +
                                     country + age + gender + education + income + 
                                     (1 | m),
                                   data = data.decision.waves.long, family = binomial(link = "logit"))
# random slope without demographics as reported
model.H1b.both.waves2 <- glmer(decision~  wave + energieabhaengigkeit + tax + co2 + 
                                 zeitpunkt*concern.scaled  +
                                 (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                               data = data.decision.waves.long, family = binomial(link = "logit"))
```

#### H1b both waves prereg
```{r}
tab_model(model.H1b.both.waves2.i.d)

```

#### H1b both waves random slopes
```{r}
tab_model(model.H1b.both.waves2.d)
```

#### H1b both waves random slopes no demographics

```{r}
tab_model(model.H1b.both.waves2)

```

#### point estimate H1b
```{r}

pred_H1b <- ggpredict(model.H1b.both.waves2, c("zeitpunkt", "concern.scaled[-1,1]"))  
pred_H1b <- as.data.frame(pred_H1b)
pred_H1b
```


### H1b plot both waves
```{r fig1b}
Figure1b <- plot_model(model.H1b.both.waves2, type="pred", terms=c( "concern.scaled", "zeitpunkt") , 
                       legend.title="Implementation time", colors=c("#15A000", "#0070C0"))   +
  xlim(-2,2) +
  labs(y="Predicted probabilities of supporting policy", x="Climate change concern", title = "b") +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19))

Figure1b


```

### both plots
```{r plots, fig.width = 19, fig.height = 11,}
Figure1a | Figure1b
```


### model comparison H1b versus H1 
```{r}
anova(model.both.waves.2.c, model.H1b.both.waves2.d)

```

## Longitudinal changes {.tabset}
```{r}
#### H1a ####
# We expect that the energy independence attribute will gain importance in predicting renewable energy policy support compared to t1

# interaction wave with attributes
model.both.waves.i.2 <- glmer(decision~  wave*(co2 + tax + energieabhaengigkeit + zeitpunkt)  +
                                (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                              data = data.decision.waves.long, family = binomial(link = "logit"))
### no interaction are significant, co2 is the on that comes  closest (p=0.137)

## only for energy independence because that was pre-registered
model.both.waves.e.i <- glmer(decision~  wave*energieabhaengigkeit + tax + co2 + zeitpunkt  +
                                (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                              data = data.decision.waves.long, family = binomial(link = "logit"))

model.both.waves.e.i.c <- glmer(decision~  country*wave*energieabhaengigkeit + tax + co2 + zeitpunkt  +
                                  (1 + co2 + tax + energieabhaengigkeit + zeitpunkt | m),
                                data = data.decision.waves.long, family = binomial(link = "logit"))
```

### Changes across waves
```{r}
tab_model(model.both.waves.i.2)

```

### Changes across waves for energy independence
```{r}
tab_model(model.both.waves.e.i)

```

### Changes across waves for energy independence by country
```{r}
tab_model(model.both.waves.e.i.c)

```

