---
title: "analyses product choices"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: lumen
    toc: yes
    toc_depth: 4
    number_sections: no

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(class.source = "CSSoutput",
                       eval = TRUE, echo = FALSE, include = TRUE,warning=FALSE,
                      fig.align='center', fig.show='asis',
                      size='footnotesize')

```

```{r functions, include=FALSE}
setwd("/Users/nfrings/Documents/PhD/Studies/Winter studie/results/energy-crisis")
#setwd("/Users/ninafrings/Documents/PhD/Studies/Winter studie/results")

library(tidyverse)
library(sjPlot)
library(rcompanion)
library(rstatix)
library(lmerTest); library(lme4)
library(sjlabelled)
library(sjmisc)
library(emmeans)
library("rmcorr")
library(psych)
library(patchwork)
library(afex)
library(ggeffects)

# so plot_model plots look nice
set_theme(base=theme_classic())
```



## non-cleaned for pattern people

###  wave 1: individual differences  {.tabset}
```{r load, include=FALSE}

data.product.waves.long <- read.csv("wave 2 and both waves/data/data.product.waves.long.csv")
data.product.waves.long <- data.product.waves.long[,-c(1)]

data.product.waves.long$energy.level <- factor(data.product.waves.long$energy.level, levels=c("2","1"),
                                               labels=c("High", "Low"))
data.product.waves.long$price.level <- factor(data.product.waves.long$price.level)
data.product.waves.long$gender <- factor(data.product.waves.long$gender)
data.product.waves.long$country <- factor(data.product.waves.long$country)
data.product.waves.long <- data.product.waves.long %>% filter(!gender=="non-binary")
data.product.waves.long$income <- factor(data.product.waves.long$income,
                                         levels=c( "<1'500€\n<3'100CHF","<1'500- 2'499€\n3'100-4'299CHF", "2'500- 4'000€\n<4'300- 5'899CHF", "> 4'000€\n>5'900 CHF") )

data.product.waves.long$education <- factor(data.product.waves.long$education,
                                            levels=c("no formal education", "obligatory school", "middle school" , "degree"))
data.product.waves.long$choice <- factor(data.product.waves.long$choice)
data.product.waves.long$wave <- factor(data.product.waves.long$wave, levels=c("wave1", "wave2"), labels=c("Wave 1", "Wave 2"))


```

```{r wave1, warning=FALSE}
### wave 1 ####
data.everything <- data.product.waves.long %>% filter (wave=="Wave 1")
# choice modeled with cc concern as pre-registered
model.H4a <- glmer(choice ~ price.level + energy.level*concern.scaled  +
                     country  +
                     gender + age + income + education +  (1| m),
                   data=data.everything, family="binomial")

# choice model  with judgment error (as pre-reg for wave2 with interaction)
model.H4a.c.i <- glmer(choice ~ price.level + energy.level*mean.error_scaled  +
                         country   +
                         gender + age + income + education +  (1| m),
                       data=data.everything, family="binomial")


```

####  climate change concern
CC concern interaction with energy level, with demographics and random intecept
```{r}
tab_model(model.H4a)
```

#### energy literacy 
Energy literacy interaction with energy level, with demographics and random intecept
```{r}
tab_model(model.H4a.c.i)
```


```{r}
##### for estimation binary and weight of complexity task only #####
data.everything <- read.csv("wave1 results and R/data/data.everything.csv")
data.everything <- data.everything[,-c(1)]
data.everything$energy.level <- factor(data.everything$energy.level)
data.everything$choice <- factor(data.everything$choice)
data.everything$est.binary <- factor(data.everything$est.binary)

data.everything$price.level <- factor(data.everything$price.level)
data.everything$country <- factor(data.everything$country)
data.everything$gender <- factor(data.everything$gender)
data.everything <- data.everything %>% filter(!gender=="non-binary")

data.everything$income <- factor(data.everything$income,
                                 levels=c( "<1'500€\n<3'100CHF","<1'500- 2'499€\n3'100-4'299CHF", "2'500- 4'000€\n<4'300- 5'899CHF", "> 4'000€\n>5'900 CHF") )
data.everything$education <- factor(data.everything$education,
                                    levels=c("no formal education", "obligatory school", "middle school" , "degree"))
# with impact strength dimension (originally H4b)
model.H4a1 <- glmer(choice ~ price.level + energy.level + V2 +
                      country    +
                      gender + age + income + education +  (1| ResponseId),
                    data=data.everything, family="binomial")

# choice model  with  binary over or underestimation as pre-reg in wave 2
data.everything$est.binary <- factor(data.everything$est.binary)
model.H4a.2 <- glmer(choice ~ price.level + energy.level + est.binary  +
                       country  +
                       gender + age + income + education +  (1 | ResponseId),
                     data=data.everything, family="binomial")
### no effect of impact strength dimension (= V2)


```

#### Impact strength as main effect  
```{r}
tab_model(model.H4a1)
```

#### Binary over / under estimation as pre-reg in wave 1
```{r}
tab_model(model.H4a.2)
```

###  wave 2: individual differences  {.tabset}
```{r}
##### wave 2 #####
data.everything.w2 <- data.product.waves.long %>% filter(wave=="Wave 2")

### judgment error model
# as pre-regsitered
model.H4.wave2.error <- glmer(choice ~ price.level + energy.level*mean.error_scaled +
                                country  +
                                gender + age + income + education  +
                                (1| m),
                              data=data.everything.w2, family="binomial")

## cc concern model
model.H4.wave2.concern <- glmer(choice ~ price.level + energy.level*concern.scaled +
                                  country  +
                                  gender + age + income + education  +
                                  (1| m),
                                data=data.everything.w2, family="binomial")

```

#### Climate change concern
```{r}
tab_model(model.H4.wave2.concern)

```

#### Energy literacy
```{r}
tab_model(model.H4.wave2.error)

```


### Both waves together  
```{r}
#### product both waves together ####

### wave  but no interaction
model.product.waves <- glmer(choice ~ wave + country + energy.level  +  price.level +
                               age + gender + education + income  +
                               (1  |  m),
                             data = data.product.waves.long, family = binomial(link = "logit"))

#### cc concern across both waves
model.H4a.both <- glmer(choice ~ price.level + energy.level*concern.scaled  +
                          country  + wave +
                          gender + age + income + education +  (1| m),
                        data=data.product.waves.long, family="binomial")
```

#### Basic model
```{r}
tab_model(model.product.waves)

```

#### Climate change concern {.tabset}

##### cc concern model
```{r}
tab_model(model.H4a.both)
```

##### cc concern plot 
```{r}
plot_model(model.H4a.both,type="pred",terms=c("concern.scaled","energy.level"),
                    colors=c( "#15A000", "#0070C0")) +
                    xlim(-1.5, 1.5) +
                    labs(x="Climate change concern", y= "Predicted prob. of energy efficient choice",title="d", color=paste0("Energy efficiency", "\n" ,"difference in choice") ) + ylim(0,1) +
                    theme(plot.caption = element_text(hjust = 0),
                    plot.title.position = "plot",
                    plot.caption.position =  "plot",
                    plot.title = element_text(size = 23, face = "bold"),
                    axis.title  = element_text(size = 23),
                    axis.text = element_text(size = 21),
                    legend.title = element_text(size = 19, face="plain"),
                    strip.text  = element_text(size = 19, face="plain"),
                    legend.text = element_text(size = 19))
  
```

##### cc concern point estimates 
```{r}

pred_H4a.c <- ggpredict(model.H4a.both, c("energy.level", "concern.scaled[-1,1]"))  
pred_H4a.c <- as.data.frame(pred_H4a.c)
print(pred_H4a.c)
```

#### Energy literacy  {.tabset}

##### energy literacy model
```{r}
### across both waves judgment error
model.H4a.error.both <- glmer(choice ~ price.level + energy.level* mean.error_scaled  +
                                country  + wave +
                                gender + age + income + education +  (1| m),
                              data=data.product.waves.long, family="binomial")
tab_model(model.H4a.error.both)

```


##### energy literacy plot

```{r}
plot_model(model.H4a.error.both,
                    type="pred",terms=c("mean.error_scaled","energy.level"),
                    colors=c( "#15A000", "#0070C0")) + xlim(-1.5, 1.5) +
  labs(x="Judgment error",  y= "Predicted prob. of energy efficient choice", title="c", 
       color=paste0("Energy efficiency", "\n" ,"difference in choice") ) + ylim(0,1) +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        strip.text  = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19))

```


##### energy literacy model point estimates 

```{r}

pred_H4a.e <- ggpredict(model.H4a.error.both, c("energy.level", "mean.error_scaled[-1,1]"))  
pred_H4a.e <- as.data.frame(pred_H4a.e)
print(pred_H4a.e)
```

#### Model comparisons:
1.  Basic model versus model with cc concern &interaction
2.  Basic model versus model with energy literacy & interaction  

```{r}

# model with neither = model.product.waves
anova(model.product.waves, model.H4a.both)
anova(model.product.waves, model.H4a.error.both)
# both models signficantly betterr than without
```
  
  
```{r}
## graphical representation of means ####
data.product.waves.long$choice.n <- as.numeric(as.character(data.product.waves.long$choice))
data.product.waves.sum1<- groupwiseSum(choice.n ~ wave + energy.level + country + m,
                                       data=data.product.waves.long)
data.product.waves.sum1$percent <- data.product.waves.sum1$Sum / data.product.waves.sum1$n
data.product.waves.mean1<- groupwiseMean(percent ~ wave + energy.level + country,
                                         data=data.product.waves.sum1)

data.product.waves.mean1$perc <- data.product.waves.mean1$Mean*100
data.product.waves.mean1$Trad.upper <- data.product.waves.mean1$Trad.upper*100
data.product.waves.mean1$Trad.lower <- data.product.waves.mean1$Trad.lower*100


```

## cleaned of pattern people

```{r pattern, include=FALSE}
data.accuracy.pattern <- read.csv("wave 2 and both waves/data/accuracy.patterns.csv")

data.product.waves.long_clean <- data.product.waves.long[!c(data.product.waves.long$m %in% data.accuracy.pattern$m), ]

```

###  wave 1 cleaned: individual differences  {.tabset}

```{r}
### wave 1 ####
data.everything_clean <- data.product.waves.long_clean %>% filter (wave=="Wave 1")
# choice modeled with cc concern as pre-registered
model.H4a <- glmer(choice ~ price.level + energy.level*concern.scaled  +
                     country  +
                     gender + age + income + education +  (1| m),
                   data=data.everything_clean, family="binomial")

# choice model  with judgment error (as pre-reg for wave2 with interaction)
model.H4a.c.i <- glmer(choice ~ price.level + energy.level*mean.error_scaled  +
                         country   +
                         gender + age + income + education +  (1| m),
                       data=data.everything_clean, family="binomial")


```
#### cc concern
```{r}
tab_model(model.H4a)
```

#### energy literacy

```{r}
tab_model(model.H4a.c.i)

```


```{r}
##### for estimation binary and weight of complexity task only #####
data.everything <- read.csv("wave1 results and R/data/data.everything.csv")
data.everything <- data.everything[,-c(1)]
data.everything$energy.level <- factor(data.everything$energy.level)
data.everything$choice <- factor(data.everything$choice)
data.everything$est.binary <- factor(data.everything$est.binary)

data.everything$price.level <- factor(data.everything$price.level)
data.everything$country <- factor(data.everything$country)
data.everything$gender <- factor(data.everything$gender)
data.everything <- data.everything %>% filter(!gender=="non-binary")

data.everything$income <- factor(data.everything$income,
                                 levels=c( "<1'500€\n<3'100CHF","<1'500- 2'499€\n3'100-4'299CHF", "2'500- 4'000€\n<4'300- 5'899CHF", "> 4'000€\n>5'900 CHF") )
data.everything$education <- factor(data.everything$education,
                                    levels=c("no formal education", "obligatory school", "middle school" , "degree"))

data.everything_clean <- data.everything[!c(data.everything$m %in% data.accuracy.pattern$m), ]

# with impact strength dimension (originally H4b)
model.H4a1 <- glmer(choice ~ price.level + energy.level +concern.scaled  +
                      country  + V2  +
                      gender + age + income + education +  (1| ResponseId),
                    data=data.everything_clean, family="binomial")
model.H4a1.i <- glmer(choice ~ price.level + energy.level*V2  +
                      country   +
                      gender + age + income + education +  (1| ResponseId),
                    data=data.everything_clean, family="binomial")
# choice model  with  binary over or underestimation as pre-reg in wave 2
data.everything$est.binary <- factor(data.everything$est.binary)
model.H4a.2 <- glmer(choice ~ price.level + energy.level + est.binary  +
                       country  +
                       gender + age + income + education +  (1 | ResponseId),
                     data=data.everything_clean, family="binomial")
### no effect of impact strength dimension (= V2)

```

#### impact weight as main effect 
```{r}
#V2
tab_model(model.H4a1)
```
#### Impact strenght with interaction with energy level  

```{r}
# interaction V2
tab_model(model.H4a1.i)

```

#### Binary over / under estimation as pre-reg in wave 1

```{r}
# binary misestimation
tab_model(model.H4a.2)

```

### wave 2: individual differences
```{r}
##### wave 2 #####
data.everything.w2_clean <- data.product.waves.long_clean %>% filter(wave=="Wave 2")

### judgment error model
# as pre-regsitered
model.H4.wave2.error <- glmer(choice ~ price.level + energy.level*mean.error_scaled +
                                country  +
                                gender + age + income + education  +
                                (1| m),
                              data=data.everything.w2_clean, family="binomial")

## cc concern model
model.H4.wave2.concern <- glmer(choice ~ price.level + energy.level*concern.scaled +
                                  country  +
                                  gender + age + income + education  +
                                  (1| m),
                                data=data.everything.w2_clean, family="binomial")
```

#### cc concern 
```{r}
tab_model(model.H4.wave2.concern)

```

#### energy literacy
```{r}
tab_model(model.H4.wave2.error)
```


## Across both waves together, cleaned 

### Individual differences {.tabset}
#### general model
```{r}
model.product.waves_clean <- glmer(choice ~ wave + country + energy.level  +  price.level +
                               age + gender + education + income  +
                               (1  |  m),
                             data = data.product.waves.long_clean, family = binomial(link = "logit"))
tab_model(model.product.waves_clean)
```

#### with cc concern (interaction)
```{r}
#### product both waves together ####

#### cc concern across both waves
model.H4a.both_clean <- glmer(choice ~ price.level + energy.level*concern.scaled  +
                          country  + wave +
                          gender + age + income + education +  (1| m),
                        data=data.product.waves.long_clean, family="binomial")
tab_model(model.H4a.both_clean)
```

#### CC concern model plot
```{r, fig.width = 13, fig.height = 8 }
Fig3d <- plot_model(model.H4a.both_clean,type="pred",terms=c("concern.scaled","energy.level"),
                    colors=c( "#15A000", "#0070C0")) +
                    xlim(-1.5, 1.5) +
                    labs(x="Climate change concern", y= "Predicted prob. of energy efficient choice",title="d", color=paste0("Energy efficiency", "\n" ,"difference in choice") ) + ylim(0,1) +
                    theme(plot.caption = element_text(hjust = 0),
                    plot.title.position = "plot",
                    plot.caption.position =  "plot",
                    plot.title = element_text(size = 23, face = "bold"),
                    axis.title  = element_text(size = 23),
                    axis.text = element_text(size = 21),
                    legend.title = element_text(size = 19, face="plain"),
                    strip.text  = element_text(size = 19, face="plain"),
                    legend.text = element_text(size = 19))
        
Fig3d
        
```

#### point estimates cc concern and energy.level -1 and 1
```{r}

pred_H4a.c <- ggpredict(model.H4a.both_clean, c("energy.level", "concern.scaled[-1,1]"))  
pred_H4a.c <- as.data.frame(pred_H4a.c)
pred_H4a.c


```

#### energy literacy (interaction)  
```{r}
### across both waves judgment error
model.H4a.error.both_clean <- glmer(choice ~ price.level + energy.level* mean.error_scaled  +
                                country  + wave +
                                gender + age + income + education +  (1| m),
                              data=data.product.waves.long_clean, family="binomial")
tab_model(model.H4a.error.both_clean)
```

#### Energy literacy plot  
```{r, fig.width = 13, fig.height = 8 }
Fig3c <- plot_model(model.H4a.error.both_clean,
                    type="pred",terms=c("mean.error_scaled","energy.level"),
                    colors=c( "#15A000", "#0070C0")) + xlim(-1.5, 1.5) +
  labs(x="Judgment error",  y= "Predicted prob. of energy efficient choice", title="c", 
       color=paste0("Energy efficiency", "\n" ,"difference in choice") ) + ylim(0,1) +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        strip.text  = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19))
Fig3c

```


#### point estimates energy literacy and energy.level

```{r}

pred_H4a.e <- ggpredict(model.H4a.error.both_clean, c("energy.level", "mean.error_scaled[-1,1]"))  
pred_H4a.e <- as.data.frame(pred_H4a.e)
pred_H4a.e

```

### Both plots together
```{r, fig.width = 13, fig.height = 8 }
Fig3c + Fig3d
```

### Model comparisons 
1. basic model versus cc concern cleaned
2. basic model versus energy literacy cleaned
```{r}

# model with neither = model.product.waves_clean
anova(model.product.waves_clean, model.H4a.both_clean)
anova(model.product.waves_clean, model.H4a.error.both_clean)
# both models signficantly betterr than without
```

### Graphical representation of means  
```{r, fig.width = 13, fig.height = 8 }
## graphical representation of means ####
data.product.waves.long_clean$choice.n <- as.numeric(as.character(data.product.waves.long_clean$choice))
data.product.waves.sum1<- groupwiseSum(choice.n ~ wave + energy.level + country + m,
                                       data=data.product.waves.long_clean)
data.product.waves.sum1$percent <- data.product.waves.sum1$Sum / data.product.waves.sum1$n
data.product.waves.mean1<- groupwiseMean(percent ~ wave + energy.level + country,
                                         data=data.product.waves.sum1)

data.product.waves.mean1$perc <- data.product.waves.mean1$Mean*100
data.product.waves.mean1$Trad.upper <- data.product.waves.mean1$Trad.upper*100
data.product.waves.mean1$Trad.lower <- data.product.waves.mean1$Trad.lower*100

Fig3a <- ggplot(data.product.waves.mean1, aes(x=wave, y=perc, fill=energy.level)) +
  geom_bar(stat="identity", position="dodge") +
  facet_wrap(country ~.) +   ylim(0,100) + labs(fill=paste0("Energy efficiency", "\n" ,"difference in choice"), x="Assessment waves",
                                                title="a", y="Mean percentage of energy efficient choices") +
  geom_errorbar(aes(ymin=Trad.lower, ymax=Trad.upper), position=position_dodge(0.9),  width=0.2) +
  geom_text(aes(label=paste0(sprintf("%.1f",perc),"%")),position=position_dodge(0.9),  vjust=-2, size=9) +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        strip.text  = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19)) +
  scale_fill_manual(values =c("#15A000", "#0070C0"))

Fig3a
```

## H5 with real energy price data
```{r}
### energy data
data.energy.plz.total.id <- read.csv( "wave 2 and both waves/data/data.energy.plz.total.id.csv", dec=".")

mean(data.energy.plz.total.id$price.diff) + 3*sd(data.energy.plz.total.id$price.diff)
# mean +- 3* sd = 21.05042

data.energy.plz.total.id.exc <- data.energy.plz.total.id %>% filter(price.diff<= 21.05042 )

# relative price diff
data.energy.plz.total.id.exc$rel_price_difference <- scale(data.energy.plz.total.id.exc$price.diff)[,1]
data.energy.plz.total.id.exc$rel_price_2023 <- scale(data.energy.plz.total.id.exc$Preis2023)[,1]

#### merge CH longitduinal data with energy price data
data.product.waves.long.ch <- data.product.waves.long %>% filter(country=="Switzerland")

# merge

# Preis 2022 als Grundlage und  price change  (difference abs) oder relativ als percent * wave
data.product.waves.long.price <- merge(data.product.waves.long.ch, data.energy.plz.total.id.exc, by=c("m"))
data.product.waves.long.price$wave <- factor(data.product.waves.long.price$wave)
data.product.waves.long.price$choice <- factor(data.product.waves.long.price$choice)

data.product.waves.long.price$income  <- factor(data.product.waves.long.price$income,
                                                levels=c( "<1'500€\n<3'100CHF","<1'500- 2'499€\n3'100-4'299CHF", "2'500- 4'000€\n<4'300- 5'899CHF", "> 4'000€\n>5'900 CHF"),
                                                labels = c("<3'100CHF", "3'100- 4'299CHF", "4'300- 5'899CHF", ">5'900 CHF"))
data.product.waves.long.price$gender <- factor(data.product.waves.long.price$gender)
data.product.waves.long.price$education <- factor(data.product.waves.long.price$education)


data.product.waves.long.price_clean <- data.product.waves.long.price[!c(data.product.waves.long.price$m %in% data.accuracy.pattern$m), ]


```

### H5 pre-registered model
= with 3-way interaction, concern scaled and mean error scaled, and demographics
```{r}
model.choice.price.diff.prereg_clean  <- glmer(choice ~  rel_price_difference*wave*energy.level    +
                                           concern.scaled  + mean.error_scaled+ price.level +
                                           age +
                                           gender + income + education +
                                           (1 |m) ,
                                         data=data.product.waves.long.price_clean, family = binomial(link = "probit"))
#tab_model(model.choice.price.diff.prereg_clean)
Anova(model.choice.price.diff.prereg_clean, type=2)

```


Point estimates for the predicted choice probablity for the relative price differences (-1sd, mean, +1sd)
```{r}
pred_2 <- ggemmeans(model.choice.price.diff.prereg_clean, c("wave", "rel_price_difference[-1,0,+1]")) %>% rename(rel_price_difference = group)
pred_2 <- as.data.frame(pred_2)
pred_2$wave2 <- c(0.78,1,1.22, 1.75, 1.97, 2.19)
pred_2
```

### Plot for H5
```{r, fig.width = 13, fig.height = 8 }

Fig3b <- ggplot(pred_2, aes(x = wave2, y = predicted)) + scale_color_manual(values=c("#F6BE00", "#ff8c00", "#a50000"))+scale_fill_manual(values=c("#F6BE00", "#ff8c00", "#a50000"))+
    geom_bar(stat="identity", position="dodge", aes( fill=rel_price_difference), width=.2) +
    geom_errorbar(aes(ymin=conf.low, ymax=conf.high), position=position_dodge(0.9), width=0.1)     +
    theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 23, face = "bold"),
          axis.title  = element_text(size = 23),
          axis.text = element_text(size = 21),
          legend.title = element_text(size = 19, face="plain"),
          strip.text  = element_text(size = 19, face="plain"),
          legend.text = element_text(size = 19)) + 
    ylim(0,1)+ 
    labs(fill=paste0("Relative energy", "\n", "price difference"), y="Predicted prob. of energy efficient choice",
         x="Assessment waves", title="b") + scale_x_discrete(limits=c("Wave 1", "Wave 2"))
         
```
/

All plots together
```{r, fig.width = 20, fig.height = 14 }
All.fig <- (Fig3a | Fig3b)  / (Fig3c + Fig3d)
All.fig
```



#### controlling for 2022 energy price
```{r}
## controlling for price 2022
model.choice.price.diff.prereg.2 <- glmer(choice ~  rel_price_difference*wave*energy.level   + price.level +
                                            Preis2022 +
                                            concern.scaled  + mean.error_scaled+
                                            age + gender + income + education +
                                            (1 |m) ,
                                          data=data.product.waves.long.price, family = binomial(link = "logit"))
tab_model(model.choice.price.diff.prereg.2)
```

#### price effect only in wave 2
```{r}

data.product.waves.long.price_clean.wave2 <- data.product.waves.long.price_clean %>% filter(wave=="Wave 2")

model.choice.price.diff.w2 <- glmer(choice ~  rel_price_difference*energy.level    +
                                           concern.scaled  + mean.error_scaled+ price.level +
                                           age +
                                           gender + income + education +
                                           (1 |m) ,
                                         data=data.product.waves.long.price_clean, family = binomial(link = "probit"))
tab_model(model.choice.price.diff.w2)
Anova(model.choice.price.diff.w2, type=2)

plot_model(model.choice.price.diff.w2, type="emm", terms=c("energy.level","rel_price_difference"), colors=c("#F6BE00", "#ff8c00", "#a50000"))

```


#### absolute price effect
```{r}


model.choice.price.diff.w2.2 <- glmer(choice ~  price.diff*wave*energy.level    +
                                           concern.scaled  + mean.error_scaled+ price.level +
                                           age +
                                           gender + income + education + (1 |m) ,
                                    data=data.product.waves.long.price_clean, family = binomial(link = "probit"))
Anova(model.choice.price.diff.w2.2, type=2)

plot_model(model.choice.price.diff.w2.2, type="emm", terms=c("energy.level","price.diff"), colors=c("#F6BE00", "#ff8c00", "#a50000"))

```

```{r energy.price}
## distribution of energy difference
data.energy.plz.total.id.exc_clean <- data.energy.plz.total.id.exc[!c(data.energy.plz.total.id.exc$m %in% data.accuracy.pattern$m), ]
ggplot(data.energy.plz.total.id.exc_clean, aes(x=rel_price_difference)) +
  geom_histogram(bins=100) + theme_minimal() +
    theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 23, face = "bold"),
          axis.title  = element_text(size = 23),
          axis.text = element_text(size = 21),
          legend.title = element_text(size = 19, face="plain"),
          strip.text  = element_text(size = 19, face="plain"),
          legend.text = element_text(size = 19)) + 
    labs(y="amount of individuals experiencing this energy price difference",
         x="relative energy price difference") 
         

```


