---
title: "analyses judgment new"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: lumen
    toc: yes
    toc_depth: 4
    number_sections: no

---




```{r setup, include=FALSE}
knitr::opts_chunk$set(class.source = "CSSoutput",
                      eval = TRUE, echo = FALSE, include = TRUE,warning=FALSE,
                      fig.align='center', fig.show='asis', fig.width = 16, fig.height = 10,
                      size='footnotesize')

```

```{r, include=FALSE}
setwd("/Users/nfrings/Library/Mobile Documents/com~apple~CloudDocs/Documents/PhD/Studies/Winter studie/results")
#setwd("/Users/ninafrings/Documents/PhD/Studies/Winter studie/results")

library(tidyverse)
library(sjPlot)
library(rcompanion)
library(rstatix)
library(lmerTest); library(lme4)
library(sjlabelled)
library(sjmisc)
library(emmeans)
library("rmcorr")
library(psych)
library(patchwork)
library(afex)
library(ClinSigMeasures)
library(prettydoc)
library(ggeffects)

# so plot_model plots look nice
set_theme(base=theme_classic())
```


```{r}
#### accuracy wave 1 ####

data.accuracy.pattern <- read.csv("wave 2 and both waves/data/accuracy.patterns.csv")

data.accuracy.long.total <- read.csv("wave1 results and R/data/data.accuracy.long.total.csv")
data.accuracy.long.total <- data.accuracy.long.total[, -c(1)]


data.accuracy.long.total$behavior.label <- factor(data.accuracy.long.total$behavior,
                                                  levels=c("fridge_eff", "dishwasher", "washing", "hairdryer",
                                                           "light_eff", "heating", "dryer", "shower"),
                                                           labels=c("fridge", "dishwasher", "washing", "hairdryer",
                                                           "light", "heating", "dryer", "shower" ))
data.accuracy.long.total <- data.accuracy.long.total %>% filter(!gender=="non-binary")


#data.accuracy.long.total.c <-  data.accuracy.long.total %>% filter(!c(behavior=="light_eff" | behavior=="fridge_eff"))

#data.accuracy.long.total.c <- data.accuracy.long.total
data.accuracy.long.total$impact <- factor(data.accuracy.long.total$behavior.label,
                                          levels = c( "dishwasher", "washing", "hairdryer", "fridge",
                                                      "heating", "dryer", "shower", "light"),
                                          labels=c( "low","low", "low","low",
                                                    "high", "high", "high", "low"))
data.accuracy.long.total_clean <- data.accuracy.long.total[!c(data.accuracy.long.total$m %in% data.accuracy.pattern$m), ]

## wave 2

data.accuracy.w2.long.total <- read.csv("wave 2 and both waves/data/data.accuracy.w2.long.total.csv")
data.accuracy.w2.long.total <- data.accuracy.w2.long.total[, -c(1)]
data.accuracy.w2.long.total$gender <- factor(data.accuracy.w2.long.total$gender)
data.accuracy.w2.long.total <- data.accuracy.w2.long.total %>% filter(!gender=="non-binary")

data.accuracy.w2.long.total$income <- factor(data.accuracy.w2.long.total$income)
data.accuracy.w2.long.total$education <- factor(data.accuracy.w2.long.total$education)


data.accuracy.w2.long.total$behavior.label <- factor(data.accuracy.w2.long.total$behavior)
data.accuracy.w2.long.total$impact <- factor(data.accuracy.w2.long.total$behavior.label,
                                          levels = c( "dishwasher", "washing", "hairdryer", "fridge",
                                                      "heating", "dryer", "shower", "light"),
                                          labels=c( "low","low", "low","low",
                                                    "high", "high", "high", "low"))
                                                    
data.accuracy.w2.long.total_clean <- data.accuracy.w2.long.total[!c(data.accuracy.w2.long.total$m %in% data.accuracy.pattern$m), ]


#### across waves comparison ANOVA ####
#### long format
data.accuracy.waves.long <- read.csv("wave 2 and both waves/data/data.accuracy.waves.long.csv")

data.accuracy.waves.long$wave <- factor(data.accuracy.waves.long$wave)
data.accuracy.waves.long <- data.accuracy.waves.long %>% filter(!gender=="non-binary")
data.accuracy.waves.long_clean <- data.accuracy.waves.long[!c(data.accuracy.waves.long$m %in% data.accuracy.pattern$m), ]

```

## H3a frequency wave 1  {.tabset}
```{r}
data.accuracy.waves.long.total  <- read.csv("wave 2 and both waves/data/data.accuracy.waves.long.total.csv")
data.accuracy.waves.long.total <- data.accuracy.waves.long.total[, -c(1)]

data.accuracy.waves.long.total<- data.accuracy.waves.long.total %>% filter(!gender=="non-binary")
data.accuracy.waves.long.total_clean <-   data.accuracy.waves.long.total[!c( data.accuracy.waves.long.total$m %in% data.accuracy.pattern$m), ]
```


### H3a 
```{r}
#### H3 a frequency ####

data.accuracy.test.freq <- read.csv("wave1 results and R/data/data.accuracy.frequency.csv")
data.accuracy.test.freq <- data.accuracy.test.freq[, -c(1)]
data.accuracy.test.freq <- data.accuracy.test.freq  %>% filter(!gender=="non-binary")

model.accuracy.freq2 <- lm(mean.abs.error ~ gender + age + country + income.wave1 + education +
                             climate_concern + mean.freq.clean  ,
                           data= data.accuracy.test.freq )
tab_model(model.accuracy.freq2)

```


### H3a cleaned     

```{r}
### cleaned for pattern people!!
data.accuracy.test.freq_clean <- data.accuracy.test.freq[!c(data.accuracy.test.freq$m %in% data.accuracy.pattern$m), ]

model.accuracy.freq2 <- lm(mean.abs.error ~ gender + age + country + income.wave1 + education +
                             climate_concern + mean.freq.clean  ,
                           data= data.accuracy.test.freq_clean )
tab_model(model.accuracy.freq2)

```
    
    
  
## H3b wave 2

###  certainty and accuracy {.tabset}
#### Model with certainty and numeracy  
```{r}
#H3b: We will explore the relationship between confidence in the estimates ####
#and the accuracy of estimates between and within participants.

model.H3b.w2.d <- lmer(absolute.error.log ~ certainty + numeracy.f  +
                         education + country + gender + income  + age + concern.scaled +
                         (1 |m) + (1 |behavior),
                       data= data.accuracy.w2.long.total)
tab_model(model.H3b.w2.d)
```

#### Model with exponential certainty
```{r}
model.accuracy.exp <- lmer(absolute.error.log ~ certainty + numeracy.f  + I(certainty^2) +
                             education + country + gender + income  + age + concern.scaled+
                             (1 |m) + (1 |behavior),
                           data= data.accuracy.w2.long.total)

tab_model(model.accuracy.exp)
plot_model(model.accuracy.exp, type="pred", terms=c("certainty"), color="darkgrey") 
```

#### H3b cleaned
Model with certainty and numeracy  
```{r}
model.H3b.w2.d <- lmer(absolute.error.log ~ certainty + numeracy.f  +
                         education + country + gender + income  + age + concern.scaled +
                         (1 |m) + (1 |behavior),
                       data= data.accuracy.w2.long.total_clean)
tab_model(model.H3b.w2.d)
```

#### H3b plot (cleaned)
```{r}
plot_model(model.H3b.w2.d, type="pred", terms=c("certainty"), color="darkgrey") 
```

#### H3b cleaned, exponential
```{r}

model.accuracy.exp <- lmer(absolute.error.log ~ certainty + numeracy.f  + I(certainty^2) +
                             education + country + gender + income  + age + concern.scaled+
                             (1 |m) + (1 |behavior),
                           data= data.accuracy.w2.long.total_clean)

tab_model(model.accuracy.exp)
```
#### H3b (cleaned) exponential plot
```{r}
plot_model(model.accuracy.exp, type="pred", terms=c("certainty"), color="darkgrey") 

```


## Judgment estimates and actual values both waves together

### cleaned for pattern people Fig 2a

```{r, include=FALSE}
### cleaned for pattern people!!


### both waves in one plot #####
data.accuracy.w2.long.2 <- data.accuracy.w2.long.total %>% select(m, behavior, numeracy.f,  actual, estimate) %>%
  rename(estimate.wave2 = estimate)

data.accuracy.long.2 <- data.accuracy.long.total %>% select(m, behavior, actual, estimate,country) %>%
  rename(estimate.wave1 = estimate)
data.accuracy.long.2$behavior <- factor(data.accuracy.long.2$behavior ,
                                        levels=c( "dishwasher", "washing", "hairdryer", "fridge_eff",
                                                  "heating", "dryer", "shower", "light_eff"),
                                        labels=c( "dishwasher", "washing", "hairdryer", "fridge",
                                                  "heating", "dryer", "shower", "light"))

accuracy.waves <- merge(data.accuracy.w2.long.2, data.accuracy.long.2, by=c("m", "behavior", "actual"))
accuracy.waves.long <- pivot_longer(accuracy.waves,5:6, names_to = "wave", values_to = "estimate" )



### cleaned for pattern people!!
accuracy.waves.long_clean <- accuracy.waves.long[!c(accuracy.waves.long$m %in% data.accuracy.pattern$m), ]

#accuracy.waves.long.ch <- accuracy.waves.long %>% filter(country=="Switzerland")
data.estimate.waves <- groupwiseMean(estimate ~ behavior + wave  ,
                                     data =accuracy.waves.long_clean)

data.actual.waves <- groupwiseMean(actual ~ behavior + wave ,
                                   data =accuracy.waves.long_clean,
                                   percentile= FALSE,
                                   traditional = FALSE)

accuracy.means.waves <- merge(data.estimate.waves, data.actual.waves, by=c("behavior", "wave","n"))
accuracy.means.waves <- accuracy.means.waves %>%
  rename(mean.actual = Mean.y,
         mean.estimate= Mean.x)

accuracy.means.waves$behavior.label <- factor(accuracy.means.waves$behavior,
                                              levels=c("dishwasher", "washing", "hairdryer", "fridge",
                                                       "light", "heating", "dryer", "shower"),
                                              labels=c("Dishwasher", "Washing", "Hairdryer", "Fridge",
                                                       "Light", "Heating", "Dryer", "Shower"))
accuracy.means.waves$wave <- factor(accuracy.means.waves$wave, levels=c("estimate.wave1", "estimate.wave2"),labels=c("Wave 1", "Wave 2"))
```


```{r}

Fig2a.c <- ggplot(accuracy.means.waves, aes(x=mean.actual, y=mean.estimate, color=behavior.label, group=wave)) +
  geom_point(size=3.8) +
  ylim(0,1600) + xlim(0,1600) + facet_wrap( wave ~.) +
  geom_errorbar(aes(ymin=Trad.lower, ymax=Trad.upper), linewidth=1.6)  +
  labs(x="Actual value", y="Mean estimate", color="Behavior", title="a") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        strip.text  = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19)) +
  geom_abline(intercept = 0, slope = 1, linetype="dashed") +
  #  scale_color_grey()
  scale_color_viridis_d()
  
Fig2a.c 
```


## misestimation of impact across waves {.tabset}

### not cleaned
```{r, include=FALSE}
### both waves 
data.accuracy.waves.long.total2 <- data.accuracy.waves.long.total  %>%
  mutate(mis.estimation.wave1 = estimate.wave1/actual,
  mis.estimation.wave2 = estimate.wave2/actual)
data.accuracy.waves.long.total2.l <- pivot_longer(data.accuracy.waves.long.total2,cols=c(mis.estimation.wave1, mis.estimation.wave2), names_to = "wave", values_to = "mis.estimation" )
data.accuracy.waves.long.total2.l$wave <- factor(data.accuracy.waves.long.total2.l$wave, levels=c("mis.estimation.wave1", "mis.estimation.wave2"), labels=c("wave1", "wave2"))


accuracy.waves.impact.t <- groupwiseMean(mis.estimation ~impact + wave,
data= data.accuracy.waves.long.total2.l)
accuracy.waves.impact.t$Mean.2 <- 1/accuracy.waves.impact.t$Mean
accuracy.waves.impact.t$Trad.lower2 <- 1/accuracy.waves.impact.t$Trad.lower
accuracy.waves.impact.t$Trad.upper2 <- 1/accuracy.waves.impact.t$Trad.upper

```

```{r}
accuracy.waves.impact.t

accuracy.waves.impact <- groupwiseMean(mis.estimation ~impact + wave + country + m,
data= data.accuracy.waves.long.total2.l)
t.test(data.accuracy.waves.long.total2.l$mis.estimation ~ data.accuracy.waves.long.total2.l$wave, paired=TRUE)

model.impact.1 <- lmer(Mean ~impact*wave + country + (1|m), accuracy.waves.impact,   
  contrasts = list(
    impact = "contr.sum",
    wave = "contr.sum") )
tab_model(model.impact.1)



```

###  cleaned 

```{r, include=FALSE}
### both waves 

#data.accuracy.waves.long.total_clean <-   data.accuracy.waves.long.total[!c( data.accuracy.waves.long.total$m %in% data.accuracy.pattern$m), ]

data.accuracy.waves.long.total_clean <- data.accuracy.waves.long.total_clean %>%
  mutate(mis.estimation.wave1 = estimate.wave1/actual,
  mis.estimation.wave2 = estimate.wave2/actual)
data.accuracy.waves.long.total_clean2 <- pivot_longer(data.accuracy.waves.long.total_clean,cols=c(mis.estimation.wave1, mis.estimation.wave2), names_to = "wave", values_to = "mis.estimation" )
data.accuracy.waves.long.total_clean2$wave <- factor(data.accuracy.waves.long.total_clean2$wave, levels=c("mis.estimation.wave1", "mis.estimation.wave2"), labels=c("wave1", "wave2"))


accuracy.waves.impact.t <- groupwiseMean(mis.estimation ~impact + wave,
data= data.accuracy.waves.long.total_clean2)
accuracy.waves.impact.t$Mean.2 <- 1/accuracy.waves.impact.t$Mean
accuracy.waves.impact.t$Trad.lower2 <- 1/accuracy.waves.impact.t$Trad.lower
accuracy.waves.impact.t$Trad.upper2 <- 1/accuracy.waves.impact.t$Trad.upper


```

 
```{r}
accuracy.waves.impact.t

t.test(data.accuracy.waves.long.total_clean2$mis.estimation ~ data.accuracy.waves.long.total_clean2$wave, paired=TRUE)
data.accuracy.waves.long.total_clean2$log.mis.estimation <- log10(data.accuracy.waves.long.total_clean2$mis.estimation)

accuracy.waves.impact.c <- groupwiseMean(log.mis.estimation ~impact + wave + country + m,
data= data.accuracy.waves.long.total_clean2)

model.impact <- lmer(Mean ~impact*wave + country + (1|m), accuracy.waves.impact.c,   
  contrasts = list(
    impact = "contr.sum",
    wave = "contr.sum") )
tab_model(model.impact)

model.impact.2 <- lmer(log.mis.estimation ~impact*wave + country + (1|m) + (1|behavior.label), data.accuracy.waves.long.total_clean2,   
  contrasts = list(
    impact = "contr.sum",
    wave = "contr.sum") )
tab_model(model.impact.2)

```


## Mean judgment error across waves by numeracy 

### witout pattern people fig 2b
```{r}

data.accuracy.waves.mean <- groupwiseMean(mean.abs.error ~ wave + country + numeracy.f,
                                          data= data.accuracy.waves.long_clean)
data.accuracy.waves.mean$wave <- factor(data.accuracy.waves.mean$wave, levels=c("wave1","wave2"),
                                        labels=c("Wave 1", "Wave 2"))
data.accuracy.waves.mean$numeracy.f <- factor(data.accuracy.waves.mean$numeracy.f, levels=c("numeracy high","numeracy low"),
                                              labels=c("Numeracy high", "Numeracy low"))

```


```{r}
Figure2b.c <- ggplot(data.accuracy.waves.mean, aes(x=wave, y=Mean, color=numeracy.f)) +
  geom_point() + ylim(0.5,0.8) +
  geom_errorbar(aes(ymin=Trad.lower, ymax=Trad.upper), width=0.2) +
  facet_wrap(country ~.) +  
  # scale_color_grey() +
  scale_color_manual(values=c("#15A000", "#0070C0")) +
  theme_minimal() + labs(y="Mean error", color="Numeracy", title="b", x="Assessment waves") +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        strip.text = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19))

Figure2b.c

```

Both judgment figures 
```{r, fig.width=22, fig.height=10}
Fig2a.c / Figure2b.c

```

## Across waves judgment error {.tabset}
same approach as misestimation for judgment error 

```{r, include=FALSE}
### both waves 


data.accuracy.waves.long.total_clean2 <- data.accuracy.waves.long.total_clean %>%
  mutate(error.wave1 = abs(log10(estimate.wave1/actual)),
  error.wave2 = abs(log10(estimate.wave2/actual) ))
data.accuracy.waves.long.total_clean2.l <- pivot_longer(data.accuracy.waves.long.total_clean2,cols=c(error.wave1, error.wave2), names_to = "wave", values_to = "error" )
data.accuracy.waves.long.total_clean2.l$wave <- factor(data.accuracy.waves.long.total_clean2.l$wave, levels=c("error.wave1", "error.wave2"), labels=c("wave1", "wave2"))
data.accuracy.waves.long.total_clean2.l$numeracy.f <- factor(data.accuracy.waves.long.total_clean2.l$numeracy.f)


accuracy.waves.error.t <- groupwiseMean(error ~numeracy.f + wave,
data= data.accuracy.waves.long.total_clean2.l)
accuracy.waves.error.t$Mean.2 <- 1/accuracy.waves.error.t$Mean
accuracy.waves.error.t$Trad.lower2 <- 1/accuracy.waves.error.t$Trad.lower
accuracy.waves.error.t$Trad.upper2 <- 1/accuracy.waves.error.t$Trad.upper


```

Models cleaned for pattern people
Model only with numeracy
```{r}
accuracy.waves.error.t

accuracy.waves.error.num <- groupwiseMean(error ~ numeracy.f + wave   + country + m,
data= data.accuracy.waves.long.total_clean2.l)

data.accuracy.waves.long.total_clean2.l$impact <- factor(data.accuracy.waves.long.total_clean2.l$impact, level=c("low", "high"),
labels=c("low impact", "high impact"))

model.error.waves.numeracy<- lmer(Mean ~numeracy.f*wave + country + (1|m), accuracy.waves.error.num)
tab_model(model.error.waves.numeracy)
plot_model(model.error.waves.numeracy,type="emm", terms=c("wave", "numeracy.f"), colors=c("#15A000", "#0070C0"))

 #impact
accuracy.waves.error.imp<- groupwiseMean(error ~ impact + wave   + country + m,
data= data.accuracy.waves.long.total_clean2.l)
model.error.waves.impact<- lmer(Mean ~impact*wave + country + (1|m), accuracy.waves.error.imp)
## impact not significant overall -> more down to numeracy


```
Model for impact

```{r}
tab_model(model.error.waves.impact)

```

Model for each judgment error
```{r}

model.error.waves.impact2 <- lmer(error ~impact*wave +numeracy.f*wave + country + (1|m) + (1|behavior.label), data.accuracy.waves.long.total_clean2.l)
tab_model(model.error.waves.impact2)

```

### Plots: Judgment error for impact of actions across waves

```{r}
pred_wave.impact <- ggemmeans(model.error.waves.impact2, c("wave", "impact")) 
pred_wave.impact <- as.data.frame(pred_wave.impact)

ggplot(pred_wave.impact, aes(x = x, y = predicted, color=group)) + scale_color_manual(values=c("#0070C0", "#15A000"))+ scale_fill_manual(values=c("#0070C0", "#15A000"))+ theme_minimal() +
    geom_point(stat="identity", position=position_dodge(0.1), size=4) +
    geom_errorbar(aes(ymin=conf.low, ymax=conf.high), position=position_dodge(0.1), width=0.1, size=1.2)     +
    theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 23, face = "bold"),
          axis.title  = element_text(size = 23),
          axis.text = element_text(size = 21),
          legend.title = element_text(size = 19, face="plain"),
          strip.text  = element_text(size = 19, face="plain"),
          legend.text = element_text(size = 19)) + 
    ylim(0.4,0.9)  + labs(x="Assessment wave", y="Mean judgment error", color="Impact of actions")

    
```


### Plot: Judgment error for numeracy across waves


```{r}
pred_num.impact <- ggemmeans(model.error.waves.impact2, c("wave", "numeracy.f")) 
pred_num.impact <- as.data.frame(pred_num.impact)

ggplot(pred_num.impact, aes(x = x, y = predicted, color=group)) + scale_color_manual(values=c("#15A000", "#0070C0"))+ scale_fill_manual(values=c("#15A000", "#0070C0"))+  theme_minimal() +
    geom_point(stat="identity", position=position_dodge(0.1), size=4) +
    geom_errorbar(aes(ymin=conf.low, ymax=conf.high), position=position_dodge(0.1), width=0.1, size=1.2)     +
    theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 23, face = "bold"),
          axis.title  = element_text(size = 23),
          axis.text = element_text(size = 21),
          legend.title = element_text(size = 19, face="plain"),
          strip.text  = element_text(size = 19, face="plain"),
          legend.text = element_text(size = 19)) + 
    ylim(0.4,0.9)  + labs(x="Assessment wave", y="Mean judgment error", color="Numeracy")

    
```

### Plot: numeracy by wave and country
```{r}
pred_num.impact.c <- ggemmeans(model.error.waves.impact2, c("wave", "numeracy.f", "country")) 
pred_num.impact.c <- as.data.frame(pred_num.impact.c)

ggplot(pred_num.impact.c, aes(x = x, y = predicted, color=group)) + scale_color_manual(values=c("#15A000", "#0070C0"))+ scale_fill_manual(values=c("#15A000", "#0070C0"))+  facet_wrap(facet~.) +  theme_minimal() +
    geom_point(stat="identity", position=position_dodge(0.1), size=4) +
    geom_errorbar(aes(ymin=conf.low, ymax=conf.high), position=position_dodge(0.1), width=0.1, size=1.2)     +
    theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 23, face = "bold"),
          axis.title  = element_text(size = 23),
          axis.text = element_text(size = 21),
          legend.title = element_text(size = 19, face="plain"),
          strip.text  = element_text(size = 19, face="plain"),
          legend.text = element_text(size = 19)) + 
    ylim(0.4,0.9) 
    
```


### Plot: Everything in one plot

```{r}
 
pred_everything <- ggemmeans(model.error.waves.impact2, c("wave", "numeracy.f", "impact", "country")) 
pred_everything <- as.data.frame(pred_everything)

ggplot(pred_everything, aes(x = x, y = predicted, color=group)) + scale_color_manual(values=c("#15A000", "#0070C0"))+ scale_fill_manual(values=c("#15A000", "#0070C0"))+ facet_wrap(panel~facet) + theme_minimal() +
    geom_point(stat="identity", position=position_dodge(0.1), size=4) +
    geom_errorbar(aes(ymin=conf.low, ymax=conf.high), position=position_dodge(0.1), width=0.1, size=1.2)     +
    theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 23, face = "bold"),
          axis.title  = element_text(size = 23),
          axis.text = element_text(size = 21),
          legend.title = element_text(size = 19, face="plain"),
          strip.text  = element_text(size = 19, face="plain"),
          legend.text = element_text(size = 19)) + 
    ylim(0.4,0.9) 
```

### Plot: Everything in one plot2
```{r}
ggplot(pred_everything, aes(x = x, y = predicted, color=facet)) + scale_color_manual(values=c("#0070C0", "#15A000"))+ scale_fill_manual(values=c("#0070C0", "#15A000"))+ facet_wrap(panel~group) + theme_minimal() +
    geom_point(stat="identity", position=position_dodge(0.1), size=4) +
    geom_errorbar(aes(ymin=conf.low, ymax=conf.high), position=position_dodge(0.1), width=0.1, size=1.2)     +
    theme(plot.caption = element_text(hjust = 0),
          plot.title.position = "plot",
          plot.caption.position =  "plot",
          plot.title = element_text(size = 23, face = "bold"),
          axis.title  = element_text(size = 23),
          axis.text = element_text(size = 21),
          legend.title = element_text(size = 19, face="plain"),
          strip.text  = element_text(size = 19, face="plain"),
          legend.text = element_text(size = 19)) + 
    ylim(0.4,0.9) 
```

## By country {.tabset}
### Switzerland

```{r}
## ch
accuracy.waves.error.num.ch <- accuracy.waves.error.num %>% filter(country=="Switzerland")

model.error.waves.impact.ch <- lmer(Mean ~ numeracy.f*wave + (1|m), accuracy.waves.error.num.ch)

tab_model(model.error.waves.impact.ch)

```
### Plot Switzerland
```{r}
plot_model(model.error.waves.impact.ch, type="pred", terms=c("wave","numeracy.f"),
colors=c("#15A000", "#0070C0") )  + ylim(0.4,0.9) + 
  theme_minimal() + labs(y="Mean error", color="Numeracy", title="in Switzerland", x="Assessment waves") +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        strip.text = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19))
```

### Germany

```{r}
accuracy.waves.error.num.de <- accuracy.waves.error.num %>% filter(!country=="Switzerland")

model.error.waves.impact.de <- lmer(Mean ~ numeracy.f*wave + (1|m), accuracy.waves.error.num.de)
tab_model(model.error.waves.impact.de)

        
```
### Plot Germany
```{r}

plot_model(model.error.waves.impact.de, type="pred", terms=c("wave","numeracy.f"),
colors=c("#15A000", "#0070C0") ) + ylim(0.4,0.9) +
  theme_minimal() + labs(y="Mean error", color="Numeracy", title="in Germany", x="Assessment waves") +
  theme(plot.caption = element_text(hjust = 0),
        plot.title.position = "plot",
        plot.caption.position =  "plot",
        plot.title = element_text(size = 23, face = "bold"),
        axis.title  = element_text(size = 23),
        axis.text = element_text(size = 21),
        legend.title = element_text(size = 19, face="plain"),
        strip.text = element_text(size = 19, face="plain"),
        legend.text = element_text(size = 19))
        
        
```


## across waves cohens q
Original pre-registered plan to compare cohens q

For high numeracy people ths difference does approach a small effect (such that the correlation between estimates and actual values ist higher in wave2)

```{r}
#H3a: We expect for accuracy to have improved from t1 to t2, such that the correlation between estimates and actual energy use is higher.
### repeated measures correlation ####

#repeated measures correlation wave 2
q2 <- rmcorr(m, estimate.log, actual.log, data=data.accuracy.w2.long.total)
# wave 2 repeated measurment cor = 0.1856733
# for high numeracy
data.accuracy.w2.long.num <- data.accuracy.w2.long.total %>% filter(numeracy.f=="numeracy high")
q2.num.high <-  rmcorr(m, estimate.log, actual.log, data=data.accuracy.w2.long.num)


## repeated measures correlation wave 1
q1 <- rmcorr(m,estimate.log, actual.log, data.accuracy.long.total)


# for high numeracy
data.high.num <- data.accuracy.w2.long.num %>% select (m)
data.high.num <- unique(data.high.num)
data.accuracy.long.num <- merge(data.accuracy.long.total , data.high.num, by="m")

q1.num.high <- rmcorr(m, estimate.log, actual.log, data=data.accuracy.long.num)
# 0.3389379
# compare wave 1 and wave2

# values from above inout below
cohens_q(q1$r, q2$r)

# https://www.ncbi.nlm.nih.gov/pmc/articles/PMC9177411/#:~:text=The%20value%20q%20is%20the,q%20%E2%89%A5%200.5%2C%20large%20effect.
# q < 0.1 = no effect,

```

high numeracy
```{r}
cohens_q(q1.num.high$r, q2.num.high$r)
```
For high numeracy people the cohens q (rounded) can be categorized as a small effect


without pattern people

```{r}
q2 <- rmcorr(m, estimate.log, actual.log, data=data.accuracy.w2.long.total_clean)

q1 <- rmcorr(m,estimate.log, actual.log, data.accuracy.long.total_clean)

# values from above inout below
cohens_q(q1$r, q2$r)
```

```{r}
data.accuracy.w2.long.num_clean <- data.accuracy.w2.long.total_clean %>% filter(numeracy.f=="numeracy high")
q2.num.high <-  rmcorr(m, estimate.log, actual.log, data=data.accuracy.w2.long.num_clean)

# for high numeracy
data.high.num_clean <- data.accuracy.w2.long.num_clean %>% select (m)
data.high.num_clean <- unique(data.high.num_clean)
data.accuracy.long.num_clean <- merge(data.accuracy.long.total_clean , data.high.num_clean, by="m")

q1.num.high <- rmcorr(m, estimate.log, actual.log, data=data.accuracy.long.num_clean)

```

high numeracy no pattern people
```{r}
cohens_q(q1.num.high$r, q2.num.high$r)
```
For high numeracy people the cohens q (rounded) can be categorized as a small effect


